Historical aerial surveys map long-term changes of forest cover and structure in the central Congo Basin

### 2020-01-30 manuscript/appendix.Rmd
minor revisions

```{r echo=FALSE, out.height='75%', fig.align="center",fig.cap="Shelves with aerial survey images at the Africa Museum archives."}
knitr::include_graphics('./figures/archives_aerial_photos_2.jpg')
```

```{r echo=FALSE, out.height='50%', fig.align="center",fig.cap="Boxplots comparing the first principal component (PC1) of a site based FOTO analysis across different forest types for both contemporary (Geo-Eye) and historical orthomosaic data."}
knitr::include_graphics('./figures/foto_bplot_psp.png')
```

>>>>

```{r echo=FALSE, out.height='75%', fig.align="center",fig.cap="Shelves with aerial survey images at the Africa Museum archives, showing vasts amounts of historical data still mostly unexplored."}
knitr::include_graphics('./figures/archives_aerial_photos_2.jpg')
```

### 2020-01-30 manuscript/appendix.tex
minor revisions

\caption{Shelves with aerial survey images at the Africa Museum archives.}\label{fig:unnamed-chunk-5}
\end{figure}

{\centering \includegraphics[width=14.58in,height=0.5\textheight]{./figures/foto_bplot_psp}

\caption{Boxplots comparing the first principal component (PC1) of a site based FOTO analysis across different forest types for both contemporary (Geo-Eye) and historical orthomosaic data.}\label{fig:unnamed-chunk-6}
\end{figure}

@@

\caption{Scatterplot comparing Above Ground Carbon and the first principal component of the FOTO analysis for contemporary Geo-Eye (left) and the historical orthomosaic (right) data. Different forest types are plotted using closed circles, closed triangles, closed squares and this for fallow, mixed mon-dominant and young-regrowth forests, respectivelly }\label{fig:unnamed-chunk-7}
\end{figure}

@@

\caption{Scatterplot comparing tree species richness and the first principal component of the FOTO analysis for contemporary Geo-Eye (left) and the historical orthomosaic (right) data. Different forest types are plotted using closed circles, closed triangles, closed squares and this for fallow, mixed mon-dominant and young-regrowth forests, respectivelly}\label{fig:unnamed-chunk-8}
\end{figure}

@@

\caption{Scatterplot comparing stem density (per ha) and the first principal component of the FOTO analysis for contemporary Geo-Eye (left) and the historical orthomosaic (right) data. Different forest types are plotted using closed circles, closed triangles, closed squares and this for fallow, mixed mon-dominant and young-regrowth forests, respectivelly}\label{fig:unnamed-chunk-9}
\end{figure}

>>>>

\caption{Shelves with aerial survey images at the Africa Museum archives, showing vasts amounts of historical data still mostly unexplored.}\label{fig:unnamed-chunk-5}
\end{figure}

@@

\caption{Scatterplot comparing Above Ground Carbon and the first principal component of the FOTO analysis for contemporary Geo-Eye (left) and the historical orthomosaic (right) data. Different forest types are plotted using closed circles, closed triangles, closed squares and this for fallow, mixed mon-dominant and young-regrowth forests, respectivelly }\label{fig:unnamed-chunk-6}
\end{figure}

@@

\caption{Scatterplot comparing tree species richness and the first principal component of the FOTO analysis for contemporary Geo-Eye (left) and the historical orthomosaic (right) data. Different forest types are plotted using closed circles, closed triangles, closed squares and this for fallow, mixed mon-dominant and young-regrowth forests, respectivelly}\label{fig:unnamed-chunk-7}
\end{figure}

@@

\caption{Scatterplot comparing stem density (per ha) and the first principal component of the FOTO analysis for contemporary Geo-Eye (left) and the historical orthomosaic (right) data. Different forest types are plotted using closed circles, closed triangles, closed squares and this for fallow, mixed mon-dominant and young-regrowth forests, respectivelly}\label{fig:unnamed-chunk-8}
\end{figure}
